If you see something, then say something to others: Complex contagions and the socially-contingent correction of misinformation

### 2018-03-29 manuscript_1.0.tex
finished up sensitivity analysis, draft updates

% declare documents and packages
\documentclass[man, 12pt, a4paper, nolmodern, noextraspace]{apa6}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{url}
\usepackage{times}
\usepackage{multirow} % multirow tables
\usepackage{arydshln} % dashline in tabular 
\renewcommand{\footnotesize}{\small} % use 11pt for footnotes
\usepackage[doublespacing]{setspace} % single space for footnotes
%\setlength{\skip\footins}{1.5pc plus 1pt} % some more space between footnote and main body
% this command put all footnotes to endnote at the end of the paper
\usepackage{endnotes}
\let\footnote\endnote

@@

\note{Word count: 6695 words \\ %\quickwordcount \\
    Draft date: \today \\
      \addvspace{.25in} 
      \textbf{Draft in progress. Please do not cite without permission.} \\
      Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}

@@

    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new \parencite[e.g.,][]{tambuscio2015fact, jin2013epidemiological, zhao2010weak}. Yet these studies have typically relied on a series of deterministic compartmental models, where diffusion dynamics were derived by differential equations representing analytic epidemic systems \parencite[e.g., see][]{zhao2010weak}. While they offer valuable insights of how information spread in a given system, they do not explicitly represent contact phenomena in a network, therefore somewhat limited in realistically representing the evolving dynamic networks on which information and behaviors are spread conditional on the network structure. Our approach was to use an exponential random graph model (ERGM) framework \parencite{robins2007introduction, morris2008specification} to simulate a series of dynamically evolving networks of different topological properties (see also below section \textit{A Stochastic Dynamic Model of Networks} for a more detail). The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles \parencite{cranmer2017navigating, robins2007introduction}, and for a simulation context, it offers a convenient yet powerful tool for independently manipulating topological structures of a evolving network based on such generative mechanisms by a researcher's choice \parencite{morris2008specification, leifeld2017temporal}. In our present application, we simulated a baseline network evolution model based on available empirical evidence along with several counterfactual models that differ in their structural characteristics, and further submit them to different stochastic models of misinformation propagations vs. corrective message adoptions. Our focus here is therefore on the role of varying network topologies and level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs. complex contagion dynamics at population level in conjunction with network topologies.

@@

	In order to explore role of network topologies in diffusion dynamic in evolving networks, we require to explicitly specify a generative principle of network structure and how such structure evolves over time. To this end, we first model formation and dissolution of citizens' political discussion ties over time through which misinformation and corrections are communicated. Using separable temporal ERGMs \parencite{krivitsky2017inference}, we estimate and simulate \emph{complete networks} that consistently reproduce observed properties of \enquote{summary statistics} drawn from egocentric network from 2009 ANES data.\footnote{	Of course, this approach requires certain assumptions in order to define a model that represents a distribution of networks that are centered on the observed properties. See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or summary target statistics, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans (i.e., main effect of partisanship, excluding Independents), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who posses multiple contacts (i.e., degree distributions).\footnote{\label{note6}	In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents. Those 2400 partisans (i.e., Democrats plus Republicans) have on average 1.975 discussion partners. Since in 2009 ANES respondents theoretically name up to three alters, this translate into egonetwork density of 0.66 (=1.975/3). For the main effect of partisanship, the marginal distribution of number of named alters by egos did not differ by partisanship, meaning that the expected mean degree for each partisan group is proportional to observed density and the size of each group. For political homophily, data indicate that 23\% of reported discussion ties exist across Democrats and Republicans. For degree distribution statistic, we supply a range of plausible yet arbitrary values since 2009 ANES does not have summary network size measure. See supplemental appendix for a detail.} Based on those information, we establish our (a) baseline small-world with political homophily network model, which consist of 2400 nodes that comprised of 1258 Democrats and 1142 Republicans. In this model, we set approximately 70\% of all exiting ties to be politically homophilous based on observed level of political homogeneity in ANES egocentric networks. We also specify a differential relationship dissolution conditional on partisan homophily of a tie \parencite[e.g., selective \enquote{unfriending}:][]{noel2011unfriending}, such that any tie within the same partisan group is expected to last longer approximately twice than cross-partisan discussion ties. 
    In addition, in order to facilitate a robust comparison of different network typologies, we additionally specify several counterfactual models of network structure: (b) Erdős–Rényi random network conditional on observed density, (c) a chain network where all nodes have no more than two connections at the same time,\footnote{	This is done by first simulating a lattice network (e.g., all nodes have exactly the same number of degrees), but due to the stochastic nature of evolving network in which ties are randomly created and dissolved, the resulting network may not have the uniform degree distribution than it would have been under strict lattice network.} and (d) a small-world network \textit{absent of partisan homophily} in tie formation and tie dissolution model. Below Figure \ref{fig:Figure1} shows the simulated cross-sectional views of networks, and Table \ref{tab:Table1} reports key descriptive statistics for each of the networks in terms of their topological properties.

@@

% Table 1 and 2.
\begin{table}[!htbp] \centering 
	\begin{minipage}{\textwidth}
    \centering
  \caption{\\ Descriptive Statistics of Cross-sectional Networks from Simulated Network Structures} 
  \label{tab:Table1} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \textbf{E-R} & \textbf{Chain} &  \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
\hline \\[-1.8ex] 
Graph density & 0.000269 & 0.000268 & 0.000277 & 0.000272 \\ 
Mean degree & 1.292 & 1.287 & 1.327 & 1.303 \\ 
Max degree & 10.0 & 4.0 & 12.0 & 12.0 \\ 
Clustering coefficients & 0.0 & 0.0 & 0.02 & 0.01 \\ 
Mean distance & 2.2 & 2.2 & 4.5 & 3.4 \\ 
Homophilous ties & 49.4\% & 50.5\% & 52.3\% & 68.5\% \\ 
Heterophilous ties & 50.6\% & 49.5\% & 47.7\% & 31.5\% \\ 
\hline \\[-1.8ex]  
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\small \vspace{0.15in}
\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily.\\ 
\end{tablenotes}
 	\end{minipage}
\bigbreak
\vspace{0.5in}
 	\begin{minipage}{\textwidth}
    \centering
\caption{\\ Misperception Recovery Scenarios by Network Topologies and Thresholds for Adopting Corrections} 
  \label{tab:Table2}

@@

	Adapting a well-known class of epidemic models, we simulated the dynamics of misinformation exposure and its correction on top of those stochastic network evolution models. We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations per each network topologies. We fit a series of SEIR (\enquote{susceptible - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on exposure and adoption of corrective messages from their peers.

@@

    To date, how many times people exactly \enquote{share} fake news and misinformation on their social networks is not yet known to public. However, a recent study by \citeauthor{allcott2017social} (\citeyear{allcott2017social}) report that, for all 65 fake news websites they have identified during 2016 election, an individual visited such sites 0.64 times per month on average, and among them 41.8\% of all visits originate from social media traffics. Similarly, \citeauthor{guess2018selective} (\citeyear{guess2018selective}) report that of 27.4\% individuals who visited fake news websites, 22.1\% of all visits originate from social media.

	We start by setting our baseline prevalence, of which we arbitrary set 15\% of partisans are initially affected by misinformation and fake news. We then set our baseline \enquote{act rate} (i.e., the average number of transmissible acts per unit time per discussion tie) by taking the average of estimates from \citeauthor{allcott2017social} (\citeyear{allcott2017social}) and from \citeauthor{guess2018selective} (\citeyear{guess2018selective}), which yields 0.164 times per hour per discussion tie.\footnote{ \citeauthor{allcott2017social} report 0.64 $\times$ 41.8\% = 0.268 shares per unit time, while \citeauthor{guess2018selective} report 0.274 $\times$ 22.1\% = 0.060 shares per unit time. This averages to 0.164 times per unit time. We additionally assume all fake news website visits are driven by information sharing on social media.} We further assume 15\% of those who initially affected are only Republicans, given that the vast majority of identified fake news articles during 2016 U.S. presidential election were overwhelmingly pro-Trump \parencite[e.g.,][]{guess2018selective}. Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their susceptible peers (i.e., those who are not yet exposed to misinformation), but those who are being mere exposed do not contribute to misinformation flow (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.

    Progression from \emph{being susceptible} (i.e., not yet being exposed) to \emph{being exposed} was determined by a simple contagion, such that a single contact with those who are infected ( = threshold of 1) is sufficient for partisans to be exposed to misinformation, yet conditional on the propensity for those who are infected to actually share such news (i.e., the probability of infection: see below). Following PEW data \parencite{pewfakenews} which suggests approximately 16\% of all partisans have had \emph{shared} fake news stories on their social network, we assume the risk of transmission of those who are already infected to share misinformation (i.e., infection probability per act) to be .16 in our simulations. Given those two parameters for the probability of infection per act (= .16) and the number of acts per unit time (= .164), the per-discussion tie transmission rate is calculated as an exponential function of the two, with a Bernoulli probability distribution controlling whether an infection event occurs. In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats (=.04 higher than Democrats) -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S. presidential election were overwhelmingly pro-Trump).

\subsection{Progression from Exposed to Infectious States}
    Progression from \emph{being exposed} to \emph{being infected} (i.e., transition between exposed to infectious states) was modeled as individual-level stochastic processes, in which there is a differential hazard of transition across partisans following a Bernoulli distribution with the transition rate parameter. Consistent with partisan motivated reasoning accounts \parencite{taber2006, nyhan2010corrections}, we set Republicans to have higher transition rates overall (= .30) than Democrats (= .07) given pro-republican misinformation exposure when they are at their mean level of accuracy motivations. We set these rate parameters based on results reported in \citeauthor{garrett2016driving} (\citeyear{garrett2016driving}), where they show that online partisan news use increases the chance of incorrectly answering the given factual knowledge question by approximately 30\% points for Republicans and 7\% point for Democrats compared to those who do not exposed to such information (see their Table S6 for a detail). Also, we assume those who score high in their accuracy motivations to have a lower transition rate regardless of their partisanship (see the online appendix for a detail), effectively treating one's partisanship and accuracy motivations as individual-level moderators of misinformation adoption process.

\subsection{Corrective Message Exposure and a Recovery from Misperceptions}
	For corrective message exposure and subsequent progression from \emph{being infected} to \emph{being recovered}, we examine two possible scenarios -- the first model closely approximate a single-shot, \emph{asocial} correction, in that the model assumes  corrections are randomly received for infected individuals, following individual-level stochastic process of adopting such corrections given exposure. This model therefore assumes no social-dynamics surrounding the misinformation correction, as typically assumed in extant experimental literature. Our second, more realistic model is more consistent with our prior discussion of simple vs. complex contagion dynamics, in that once exposed, individuals progress to recovery state when a certain proportion (= $\rho$) of his or her neighbors are sending corrective messages that debunking misinformation. We systematically vary the threshold value of $\rho$ to explore system-level consequences of social dynamics surrounding misinformation corrections. Below Table \ref{tab:Table2} lists all scenarios for the combination of network topological structure and the threshold value of $\rho$ in misperception recovery.

\section{Results}
\subsection{Simple Contagion of Misinformation Exposure}
	We first look at the simple contagion dynamics of misinformation exposure (assuming no recovery by corrections throughout the simulated time periods) and propagation rates across different network typologies over time, as depicted in Figure \ref{fig:Figure2} and in Table \ref{tab:Table3} below. The results reveal that network structures have somewhat non-trivial effects on the dynamics of misinformation propagation at population level. It seems that our baseline network model (i.e., small-world network with partisan homophily) appears to be bit better in terms of disseminating given misinformation more faster than other network structures -- that is, we do find some modest evidence that spread of simple misinformation spreads faster in our small world networks (red lines in Panel A of Figure \ref{fig:Figure2}) than in random networks (black lines in Panel A of Figure \ref{fig:Figure2}) when misinformation is spread via simple contagion (i.e., a single contact with those who are infected) followed by a individual-level stochastic progression to being infected given exposure to misinformation.

    Although differences among the cumulative exposure fractions in different network structures were not appear to be vastly different from each other (as their confidence intervals of cumulative exposure fractions significantly overlap with each other: see online supplementary materials for a detail), their exposure rates (as measured by the number of newly exposed individuals at given time point) do differ with each other as can be seen in Figure \ref{fig:Figure2} below. This was especially true between our baseline network (red lines) and random networks (black lines) as indicated in Table \ref{tab:Table4}. We used the Wilcoxon Rank Sum Test (a nonparametric test of differences of two population distributions) to test whether the two proportions of newly exposed to misinformation among the susceptible (= no. of SI flow divided by no. of susceptible per each time point) significantly differ from each other between different network topologies. The cell entries of Table \ref{tab:Table4} refer to the range of simulated time points in which two distributions of adoption rates statistically different from each other based on Wilcoxon Rank Sum Test. For instance, Table \ref{tab:Table4} indicates that from 58 to 901 time points, the distribution of the fraction of newly exposed to misinformation from ER random network and that from our baseline small-world homophily network statistically different from zero (less than .05). The results shows that across range of time points excluding the very initial stage of misinformation propagation, network structure induces statistically different adoption rates over time.

@@

    \begin{subfigure}[t]{0.8\textwidth}
        \centering
        \includegraphics[clip, width=\linewidth, page = 2]{draft/Figure_2__Prevalence.pdf} 
        \captionsetup{font=small}
        \caption*{Panel B. Susceptible - Exposed Flow, measured as the number of newly exposed to misinformation}
    \end{subfigure}

    \captionsetup{format=hang}
    \caption{Prevalence and Exposed - Infected Flow of Misinformation Over Time (Assuming No Recoveries) by Network Topologies, Averaged Over 100 Simulations.} 
    \label{fig:Figure2}
    \captionsetup{font=small}
    \caption*{Note: Straight lines in Panel A represent fraction of those who are being exposed to misinformation, whereas dotted lines represent fraction of those who are susceptible. X-axis represents simulated times (in hours) and Y-axis represents the fraction exposed to misinformation (in panel A) or rates of misinformation exposure (in panel B). Black = Erdos-Renyi random network, Grey = Chain network, Blue = Small-world absent homophily, and Red = baseline small-world homophily network.} 
\end{figure}

>>>>

% declare documents and packages
\documentclass[man, 12pt, a4paper, nolmodern, noextraspace]{apa6}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{url}
\usepackage{times}
\usepackage{booktabs}
\usepackage{multirow} % multirow tables
\usepackage{arydshln} % dashline in tabular 
\usepackage{rotating} % vertical tables
\usepackage{pdflscape} % landscape pages
\renewcommand{\footnotesize}{\small} % use 11pt for footnotes
\usepackage[doublespacing]{setspace} % single space for footnotes
%\setlength{\skip\footins}{1.5pc plus 1pt} % some more space between footnote and main body
% this command put all footnotes to endnote at the end of the paper
\usepackage{endnotes}
\let\footnote\endnote

@@

\note{Word count: 6630 words \\ %\quickwordcount \\
    Draft date: \today \\
      \addvspace{.25in} 
      \textbf{Draft in progress. Please do not cite without permission.} \\
      Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}

@@

    Utilizing simulation-based approach in modeling (mis)information propagation is not entirely new \parencite[e.g.,][]{tambuscio2015fact, jin2013epidemiological, zhao2010weak}. Yet these studies have typically relied on a series of deterministic compartmental models, where diffusion dynamics were derived by differential equations representing analytic epidemic systems \parencite[e.g., see][]{zhao2010weak}. While they offer valuable insights of how information spread in a given system, they do not explicitly represent contact phenomena in a network, therefore somewhat limited in realistically representing the evolving dynamic networks on which information and behaviors are spread conditional on the network structure. Our approach was to use an exponential random graph model (ERGM) framework \parencite{robins2007introduction, morris2008specification} to simulate a series of dynamically evolving networks of different topological properties (see also below section \textit{A Stochastic Dynamic Model of Networks} for a more detail). The ERGM framework is now regarded the most versatile yet flexible method for identifying how a given network is formed and evolves based on the underlying generative principles \parencite{cranmer2017navigating, robins2007introduction}, and for a simulation context, it offers a convenient yet powerful tool for independently manipulating topological structures of a evolving network based on such generative mechanisms by a researcher's choice \parencite{morris2008specification, leifeld2017temporal}. In our present application, we simulated a baseline network evolution model based on available empirical evidence along with several counterfactual models that differ in their structural characteristics, and further submit them to different stochastic models of misinformation propagations vs. corrective message adoptions. Our focus here is therefore on the role of varying network topologies and resulting level of attitudinal homophily as a driving force of network evolutions, and how attitudinal compositions of one's local networks (as end-results of attitudinal homophily) interactively influence simple vs. complex contagion dynamics at population level in conjunction with network topologies.

@@

  In order to explore role of network topologies in diffusion dynamic in evolving networks, we require to explicitly specify a generative principle of network structure and how such structure evolves over time. To this end, we first model formation and dissolution of citizens' political discussion ties over time through which misinformation and corrections are communicated. Using separable temporal ERGMs \parencite{krivitsky2017inference}, we estimate and simulate \emph{complete networks} that consistently reproduce observed properties of \enquote{summary statistics} drawn from egocentric network from 2009 ANES data.\footnote{  Of course, this approach requires certain assumptions in order to define a model that represents a distribution of networks that are centered on the observed properties. See \citeauthor{krivitsky2017inference} (\citeyear{krivitsky2017inference}) for a detailed discussion of this class of models and their properties.} Those observed properties, or \emph{summary target statistics}, include: density (i.e., average number of discussion partners, or \enquote{alters}), average expected number of degrees among Democrats and Republicans (i.e., main effect of partisanship, excluding Independents), the extent of partisan homophily (i.e., interaction between ego and alter partisanship), and number of people who posses multiple contacts (i.e., degree distributions).\footnote{\label{note6} In 2009 ANES panel, there are a total of 1258 self-identified Democrats and 1142 self-identified Republicans (including respective party leaners), excluding 336 Independents. Those 2400 partisans (i.e., Democrats plus Republicans) have on average 1.975 discussion partners. Since in 2009 ANES respondents theoretically name up to three alters, this translate into egonetwork density of 0.66 (=1.975/3). For the main effect of partisanship, the marginal distribution of number of named alters by egos did not differ by partisanship, meaning that the expected mean degree for each partisan group is proportional to observed density and the size of each group. For political homophily, data indicate that 23\% of reported discussion ties exist across Democrats and Republicans. For degree distribution statistic, we supply a range of plausible yet arbitrary values since 2009 ANES does not have summary network size measure. See supplemental appendix for a detail.} Based on those information, we establish our (a) baseline small-world with political homophily network model, consist of 2400 nodes that comprised of 1258 Democrats and 1142 Republicans, that closely approximate the properties of social networks documented in ANES data. In this model, we set approximately 70\% of all exiting ties to be politically homophilous based on observed level of political homogeneity in ANES egocentric networks. We also specify a differential relationship dissolution conditional on partisan homophily of a tie \parencite[e.g., selective \enquote{unfriending}:][]{noel2011unfriending}, such that any tie within the same partisan group is expected to last longer approximately twice than cross-partisan discussion ties. 
    In addition, in order to facilitate a robust comparison of different network typologies, we additionally specify several competing models of network structure: (b) Erdős–Rényi random network conditional on observed density, (c) a chain network where all nodes have no more than two connections at the same time,\footnote{ This is done by first simulating a lattice network (e.g., all nodes have exactly the same number of degrees), but due to the stochastic nature of evolving network in which ties are randomly created and dissolved, the resulting network may not have the uniform degree distribution than it would have been under strict lattice network.} and (d) a small-world network \textit{absent of partisan homophily} in tie formation and tie dissolution model. Below Figure \ref{fig:Figure1} shows the simulated cross-sectional views of networks, and Table \ref{tab:Table1} reports key descriptive statistics for each of the simulated networks from each network evolution model specification in terms of their topological properties. 

@@

% Table 1 and 2.
\begin{table}[!htbp] \centering 
  \begin{minipage}{\textwidth}
    \centering
  \caption{\\ Descriptive Statistics of Cross-sectional Networks from Simulated Network Structures} 
  \label{tab:Table1} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \textbf{E-R} & \textbf{Chain} &  \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
\hline \\[-1.8ex] 
Graph density & 0.000269 & 0.000268 & 0.000277 & 0.000272 \\ 
Mean degree & 1.292 & 1.287 & 1.327 & 1.303 \\ 
Max degree & 10.0 & 4.0 & 12.0 & 12.0 \\ 
Clustering coefficients & 0.0 & 0.0 & 0.02 & 0.01 \\ 
Mean distance & 2.2 & 2.2 & 4.5 & 3.4 \\ 
Homophilous ties & 49.4\% & 50.5\% & 52.3\% & 68.5\% \\ 
Heterophilous ties & 50.6\% & 49.5\% & 47.7\% & 31.5\% \\ 
\hline \\[-1.8ex]  
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\small \vspace{0.15in}
\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily.\\ 
\end{tablenotes}
  \end{minipage}
\bigbreak
\vspace{0.5in}
  \begin{minipage}{\textwidth}
    \centering
\caption{\\ Misperception Recovery Scenarios by Network Topologies and Thresholds for Adopting Corrections, Correction Probability = 0.5} 
  \label{tab:Table2}

@@

  Adapting a well-known class of epidemic models, we simulated the dynamics of misinformation exposure and its correction on top of those stochastic network evolution models. We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations. We fit a series of SEIR (\enquote{susceptible - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on exposure and adoption of corrective messages from their peers.

@@

    To date, how many times people exactly \enquote{share} fake news and misinformation on their social networks is not yet known to public. However, a recent study by \citeauthor{allcott2017social} (\citeyear{allcott2017social}) report that, for all 65 fake news websites they have identified during 2016 election, an individual visited such sites 0.64 times on average, and among them 41.8\% of all visits originate from social media traffics. Similarly, \citeauthor{guess2018selective} (\citeyear{guess2018selective}) report that of 27.4\% individuals who visited fake news websites, 22.1\% of all visits originate from social media.

  We start by setting our baseline prevalence, of which we arbitrary set 15\% of partisans are initially affected by misinformation and fake news. We then set our baseline \enquote{act rate} (i.e., the average number of transmissible acts per unit time per discussion tie) by taking the average of estimates from \citeauthor{allcott2017social} (\citeyear{allcott2017social}) and from \citeauthor{guess2018selective} (\citeyear{guess2018selective}), which yields 0.164 times per hour per discussion tie.\footnote{ \citeauthor{allcott2017social} report 0.64 $\times$ 41.8\% = 0.268 shares per unit time, while \citeauthor{guess2018selective} report 0.274 $\times$ 22.1\% = 0.060 shares per unit time. This averages to 0.164 times per unit time. We additionally assume all fake news website visits are driven by information sharing on social media.} We further assume 15\% of those who initially affected are only Republicans, given that the vast majority of identified fake news articles during 2016 U.S. presidential election were overwhelmingly pro-Trump \parencite[e.g.,][]{guess2018selective}. Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their susceptible peers (i.e., those who are not yet exposed to misinformation), but those who are being merely exposed to do not contribute to misinformation flow and propagation (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.

    Progression from \emph{being susceptible} (i.e., not yet being exposed) to \emph{being exposed} was determined by a simple contagion, such that a single contact with those who are infected ( = threshold value of 1) is sufficient for partisans to be exposed to misinformation, yet conditional on the propensity for those who are infected to actually share such news (i.e., the probability of infection: see below). Following PEW data \parencite{pewfakenews} which suggests approximately 16\% of all partisans have had \emph{shared} fake news stories on their social network, we assume the risk of transmission of those who are already infected to share misinformation (i.e., infection probability per act) to be .16 in our simulations. Combining those two parameters for the probability of infection per act (= .16) and the number of acts per unit time (= .164), the per-discussion tie transmission rate is calculated as an exponential function of the two, with a Bernoulli probability distribution controlling whether an infection event occurs stochastically. In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats (=.04 higher than Democrats) -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S. presidential election were overwhelmingly pro-Republican).

\subsection{Progression from Exposed to Infectious States}
    Progression from \emph{being exposed} to \emph{being infected} (i.e., transition between exposed to infectious states) was modeled as individual-level stochastic processes, in which there is a differential hazard of transition across partisans following a Bernoulli distribution with the transition rate parameter. Consistent with partisan motivated reasoning accounts \parencite{taber2006, nyhan2010corrections}, we set Republicans to have higher transition rates overall (= .30) than Democrats (= .07) given pro-republican misinformation exposure when they are at their mean level of accuracy motivations, where accuracy motivations are assumed to be normally distributed among population. We set these rate parameters based on results reported in \citeauthor{garrett2016driving} (\citeyear{garrett2016driving}), where they show that online partisan news use increases the chance of incorrectly answering the given factual knowledge question by approximately 30\% points for Republicans and 7\% point for Democrats compared to those who do not exposed to such information (see their Table S6 for a detail). Also, we assume those who score high in their accuracy motivations to have a lower transition rate regardless of their partisanship (see the online appendix for a detail), effectively treating one's partisanship and accuracy motivations as individual-level moderators of misinformation adoption process.

\subsection{Corrective Message Exposure and a Recovery from Misperceptions}
  For corrective message exposure and subsequent progression from \emph{being infected} to \emph{being recovered}, we examine two possible scenarios -- the first model closely approximate a single-shot, \emph{asocial} correction, in that the model assumes  corrections are randomly received for infected individuals, following individual-level stochastic process of adopting such corrections given exposure. This model therefore assumes no social-dynamics surrounding the misinformation correction, as typically assumed in extant experimental literature. Our second, more realistic model is more consistent with our prior discussion of simple vs. complex contagion dynamics, in that once exposed, individuals progress to recovery state when a certain proportion (= $\rho$) of his or her neighbors are sending corrective messages that debunking misinformation. In these scenarios, we assume approximately half of one's immediate neighbors (\enquote{alters}) who are not yet affected and/or already being recovered from misinformation send correction messages to the infected ego. We systematically vary the threshold value of $\rho$ to explore system-level consequences of social dynamics surrounding misinformation corrections. Below Table \ref{tab:Table2} lists all scenarios for the combination of network topological structure and the threshold value of $\rho$ in misperception recovery. 
\centerline{ -- Table \ref{tab:Table2} about here -- }

\section{Results}
\subsection{Simple Contagions of Misinformation Exposure}
  We first look at the simple contagion dynamics of misinformation exposure (assuming no recovery by corrections throughout the simulated time periods) and propagation rates across different network typologies over time, as depicted in Figure \ref{fig:Figure2} and in Table \ref{tab:Table3} below. The results reveal that network structures have somewhat non-trivial effects on the dynamics of misinformation propagation at population level. It seems that our baseline network model (i.e., small-world network with partisan homophily) appears to be bit better in terms of disseminating given misinformation more faster than other network structures -- that is, we do find some modest evidence that spread of simple misinformation spreads faster in our small world networks (red lines in Panel A of Figure \ref{fig:Figure2}) than in random networks (black lines in Panel A of Figure \ref{fig:Figure2}) when misinformation is spread via simple contagion (i.e., a single contact with those who are infected) followed by a individual-level stochastic progression to being infected given exposure to misinformation. 
\centerline{ -- Table \ref{tab:Table3} and Figure \ref{fig:Figure2} about here -- }

    Although differences among the cumulative exposure fractions in different network structures were not appear to be vastly different from each other (as their confidence intervals of cumulative exposure fractions significantly overlap with each other: see online supplementary materials for a detail), their exposure rates (as measured by the number of newly exposed individuals at given time point) do differ with each other as can be seen in Figure \ref{fig:Figure2} below. This was especially true between our baseline network (red lines) and random networks (black lines) as indicated in Table \ref{tab:Table4}. We used the Wilcoxon Rank Sum Test (a nonparametric test of differences of two population distributions) to test whether the two proportions of newly exposed to misinformation among the susceptible (= no. of SI flow divided by no. of susceptible per each time point) significantly differ from each other between different network topologies. The cell entries of Table \ref{tab:Table4} refer to the range of simulated time points in which two distributions of adoption rates statistically different from each other based on Wilcoxon Rank Sum Test. For instance, Table \ref{tab:Table4} indicates that from 58 to 901 time points, the distribution of the fraction of newly exposed to misinformation from ER random network and that from our baseline small-world homophily network statistically different from zero (less than .05). The results shows that across range of time points excluding the very initial stage of misinformation propagation, network structure induces statistically different adoption rates over time.    
\centerline{ -- Table \ref{tab:Table4} about here -- }

@@

    \begin{subfigure}[t]{0.8\textwidth}
        \centering
        \includegraphics[clip, width=\linewidth, page = 2]{draft/Figure_2__Prevalence.pdf} 
        \captionsetup{font=small}
        \caption*{Panel B. Incidence Rates of New Exposure to Misinformation (the number of newly exposed to misinformation)}
    \end{subfigure}

    \captionsetup{format=hang}
    \caption{Prevalence and Incidence Rates of Misinformation Over Time by Network Topologies (Assuming No Recoveries, Averaged Over 100 Simulations).} 
    \label{fig:Figure2}
    \captionsetup{font=small}
    \caption*{Note: Straight lines in Panel A represent fraction of those who are being exposed to misinformation, whereas dotted lines represent fraction of those who are susceptible. X-axis represents simulated times (in hours) and Y-axis represents the fraction exposed to misinformation (in panel A) or rates of misinformation exposure (in panel B). Red = Erdos-Renyi random network, Blue = Chain network, Green = Small-world absent homophily, and Violet = baseline small-world homophily network.} 
\end{figure}
